Adding selection to \stdpopsim: oh how the tables have turned

### 2024-11-18 analysis2_manuscript.tex
added abstract draft

% \author[1,+]{M. Elise Lauterbur}
% \author[3,*]{Ariella L. Gladstein}
 \author[4,*]{Graham Gower}
 \author[5*]{Nathaniel S. Pope}
 \author[5*]{Murillo F. Rodrigues}
\author[6]{Georgia Tsambos}
\author[34]{Linh N. Tran}
\author[2]{Maria Izabel A. Cavassim}
% \author[5,7]{Jeff Adrion}
% \author[5]{Saurabh Belsare}
% \author[8]{Arjun Biddanda}
% \author[5]{Victoria Caudill}
% \author[9]{Jean Cury}
% \author[10]{Ignacio Echevarria}
% \author[11]{Benjamin C. Haller}
% \author[12,13]{Ahmed R. Hasan}
\author[14,15]{Xin Huang}
% \author[16]{Leonardo Nicola Martin Iasi}
% \author[17]{Ekaterina Noskova}
% \author[18]{Jana Obšteter}
% \author[19]{Vitor Antonio Corrêa Pavinato}
% \author[20,21]{Alice Pearson}
% \author[22,23]{David Peede}
% \author[24]{Manolo F. Perez}
\author[5]{Chris C. R. Smith}
% \author[25]{Jeffrey P. Spence}
% \author[5]{Anastasia Teterina}
\author[5]{Silas Tittes}
\author[5]{Scott T. Small}
% \author[26]{Per Unneberg}
% \author[27]{Juan Manuel Vazquez}
% \author[28]{Ryan K. Waples}
% \author[29]{Anthony Wilder Wohns}
% \author[30]{Yan Wong}
% \author[31]{Franz Baumdicker}
% \author[32]{Reed A. Cartwright}
% \author[33]{Gregor Gorjanc}
\author[4]{Kirk E. Lohmueller}
\author[34]{Ryan N. Gutenkunst}
\author[30]{Jerome Kelleher}
\author[35]{Aaron P. Ragsdale}

@@

\section*{Abstract}

>>>>

% \author[1,+]{M. Elise Lauterbur}
% \author[3,*]{Ariella L. Gladstein}
 \author[4,*]{Graham Gower}
 \author[5*]{Nathaniel S. Pope}
 \author[5*]{Murillo F. Rodrigues}
 \author[5*]{Silas Tittes}
\author[6]{Georgia Tsambos}
\author[34]{Linh N. Tran}
\author[2]{Maria Izabel A. Cavassim}
% \author[5,7]{Jeff Adrion}
% \author[5]{Saurabh Belsare}
% \author[8]{Arjun Biddanda}
% \author[5]{Victoria Caudill}
% \author[9]{Jean Cury}
% \author[10]{Ignacio Echevarria}
% \author[11]{Benjamin C. Haller}
% \author[12,13]{Ahmed R. Hasan}
\author[14,15]{Xin Huang}
% \author[16]{Leonardo Nicola Martin Iasi}
% \author[17]{Ekaterina Noskova}
% \author[18]{Jana Obšteter}
% \author[19]{Vitor Antonio Corrêa Pavinato}
% \author[20,21]{Alice Pearson}
% \author[22,23]{David Peede}
% \author[24]{Manolo F. Perez}
\author[5]{Chris C. R. Smith}
% \author[25]{Jeffrey P. Spence}
% \author[5]{Anastasia Teterina}

\author[5]{Scott T. Small}
% \author[26]{Per Unneberg}
% \author[27]{Juan Manuel Vazquez}
% \author[28]{Ryan K. Waples}
% \author[29]{Anthony Wilder Wohns}
% \author[30]{Yan Wong}
% \author[31]{Franz Baumdicker}
% \author[32]{Reed A. Cartwright}
% \author[33]{Gregor Gorjanc}
\author[4]{Kirk E. Lohmueller}
\author[34]{Ryan N. Gutenkunst}
\author[30]{Jerome Kelleher}
\author[35]{Aaron P. Ragsdale}

@@

\section*{Abstract}
Natural selection is a fundamental evolutionary force that shapes patterns of genetic variation across species. 
However, simulating realistic models that incorporate both selection and complex demographic histories
has remained challenging, limiting our ability to benchmark statistical methods and explore theoretical predictions.
Here we present a major extension to the \stdpopsim{} framework that enables simulation of various modes
of natural selection, including background selection, selective sweeps, and arbitrary distributions of fitness effects (DFE).
This extension maintains \stdpopsim's core principles of reproducibility and standardization while adding support
for species-specific genomic annotations and published DFE estimates. 
We demonstrate the utility of this framework by benchmarking methods for demographic inference,
DFE estimation, and selective sweep detection across different species and scenarios. 
Our results highlight how selection can bias demographic inference, 
reveal the sensitivity of DFE inference methods to model assumptions, 
and show how genomic features like recombination rate and functional density influence power to detect selective sweeps.
This extension to \stdpopsim{} provides a powerful new resource for the population genetics community
to explore the interplay between selection and other evolutionary forces in a reproducible framework.
